Predicting The Success of The Female United States Artistic Gymnastics Team at The 2024 Paris Olympics Using Mean and Standard Deviation Derived Parameters

### 2024-01-09 manuscript/submission.tex
updating abstract outline

@@

>>>>

NOT DONE

@@

  Open with a sentence to establish the importance of the subject of the paper.
  Identify a gap in the literature to set up the background of the paper.
  Highlight the novelty/contributions of the paper.
  For application papers, allude to new discoveries and their impacts.
  For method papers, outline the essence of the methodology, and evidence from theoretical and numerical studies supporting the methods.
  It must make sense when read in isolation for those who only read the abstract, and must also provide a clear and accurate summary of the manuscript for readers who read the entire manuscript (Zeiger 2000).
